Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-23 paper/icml_drau/experiments.tex

\paragraph{Quantitative experiments.}
We benchmark DAU against DDPG on classic control benchmarks: Pendulum,
Cartpole, BipedalWalker, Ant, and Half-Cheetah environments from OpenAI Gym. On
Pendulum, Bipedal Walker and Ant, DAU is quite robust to variations of
$\deltat$ and displays reasonable performances in all cases. On the other hand,
DDPG's performance varies with $\deltat$; performance are either degraded as
$\deltat$ decreases (Ant, Cheetah), or become more variable as learning
progresses (Pendulum) with small $\deltat$'s. On Cartpole, noise dominates,
which makes interpretation difficult. On Half-Cheetah, DAU is not clearly
invariant to time discretization. This could be explained by the multiple
suboptimal regimes that coexist in the Half-Cheetah environment (walking on the
head, walking on the back).
% \begin{figure}[h]
%   \centering
%   \includegraphics[width=\columnwidth]{figs_data/cartpole_lc.png}
%   \caption{Cartpole}
%   \label{fig:cartpole-lc}
% \end{figure}

>>>>

\paragraph{Quantitative experiments.}
We benchmark DAU against DDPG on classic control benchmarks: Pendulum,
Cartpole, BipedalWalker, Ant, and Half-Cheetah environments from OpenAI Gym. On
Pendulum, Bipedal Walker and Ant, DAU is quite robust to variations of
$\deltat$ and displays reasonable performance in all cases. On the other hand,
DDPG's performance varies with $\deltat$; performance either degrades as
$\deltat$ decreases (Ant, Cheetah), or becomes more variable as learning
progresses (Pendulum) for small $\deltat$. On Cartpole, noise dominates,
making interpretation difficult. On Half-Cheetah, DAU is not clearly
invariant to time discretization. This could be explained by the multiple
suboptimal regimes that coexist in the Half-Cheetah environment (walking on the
head, walking on the back), which create discontinuities in the value
function (see Discussion).
% \begin{figure}[h]
%   \centering
%   \includegraphics[width=\columnwidth]{figs_data/cartpole_lc.png}
%   \caption{Cartpole}
%   \label{fig:cartpole-lc}
% \end{figure}
